Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-05-07 SupportingInformation.Rmd
temporary solution for unicode character in table_summary_stat_model selection results for asym sensitivity

```{r tab_summary_stat_asym_sens,echo=F,results="markup"}

knitr::kable(summary_stat, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption="summary of model selection results for asym. sensitivity \\label{tab_summary_stat_asym_sens}")
```

```{r tab_stat_npa_asym,echo=F,results="asis"}
#knitr::opts_knit$set(kable.force.latex = TRUE)
tab_asym<-readRDS("./Results/asym_sens_results/stat_npa_asym_beta_0.1_beta_0.9.RDS")

>>>>

```{r tab_summary_stat_asym_sens,echo=F,results="markup"}
cnm2<-c("b_0.1","b_0.1d_T","b_-0.1","b_-0.1d_T","b_0.9","b_0.9d_T","b_-0.9","b_-0.9d_T")
colnames(summary_stat)<-cnm2
knitr::kable(summary_stat, booktabs = T, 
             format = "pandoc",
             digits=3,
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption="summary of model selection results for asym. sensitivity \\label{tab_summary_stat_asym_sens}")
```

\newpage
```{r tab_stat_npa_asym,echo=F,results="asis"}
#knitr::opts_knit$set(kable.force.latex = TRUE)
tab_asym<-readRDS("./Results/asym_sens_results/stat_npa_asym_beta_0.1_beta_0.9.RDS")
